**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2021-08-05 paper/manuscript.tex
update figure colors,layout,order

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Colorectal cancer is one of the most common cancers in men and women and
a leading cause of cancer related deaths in the United States
(\protect\hyperlink{ref-siegel2020}{Siegel et al. 2020}). Early
detection and treatment are essential to increase survival rates, but
for a variety of reasons including the invasiveness and high cost of
screening (i.e.~colonoscopy), many people do not comply with recommended
screening guidelines (\protect\hyperlink{ref-garcuxeda2011a}{García and
Z 2011}) prompting a need for low cost, non-invasive detection methods.
A growing body of research points to the gut microbiome as a promising
target for non-invasive screening to detect screen relevant neoplasias
(neoplasms?) (SRNs) consisting of pre-cancerous polyps (i.e.~advanced
adenomas) and carcinomas. Efforts to realize the diagnostic potential of
the gut microbiome in detecting SRNs have focused on machine learning
(ML) methods using abundances from operational taxonomic unit (OTU)
classifications based on amplicon sequencing of the 16S rRNA gene \{\}.
However, whether this is the optimal taxonomic resolution for
classifying SRNs from microbiome data is unknown. Additionally, recent
work has pushed for the use of amplicon sequence variants (ASVs) to
replace OTUs for marker-gene analysis because of the improved resolution
with ASVs (\protect\hyperlink{ref-callahan2017}{Callahan, McMurdie, and
Holmes 2017}). However, whether the additional resolution provided by
ASVs is useful for ML classification is unclear \{pat preprint?\}. Since
ML classification relies on consistent differences between groups, its
possible that the resolution at the ASV level is too individualized to
accurately differentiate groups. Topçuoğlu \emph{et al}
(\protect\hyperlink{ref-topuxe7uolu2020}{Topçuoğlu et al. 2020})
recently demonstrated effective application of machine learning (ML) to
microbiome based classification problems and developed a framework for
applying ML practices in a more reproducible way (mikropml). This
analysis utilizes the reproducible framework developed by Topçuoğlu
\emph{et al} to quantify which ML method and taxonomic level produce the
best performing classifier for detecting SRNs from microbiome data.

@@

Utilizing publicly available 16S rRNA sequence data from stool of
patients with SRNs and healthy controls, we generated abundance tables
with Mothur \{\} annotated to Phylum, Class, Order, Family, Genus, OTU
and ASV levels. Using the taxonomic abundance data, we quantified how
accurately samples could be classified as ``normal'' or ``SRN''
(i.e.~advanced adenoma or carcinoma) using five machine learning methods
with the Mikropml R package (methods). Across the five machine learning
methods tested, model performance tended to increase with taxonomic
level usually peaking around genus/OTU level before dropping off
slightly with ASVs (Supplemental Figure 1). Random forest (RF) was
consistently the top performer at most taxonomic levels. Within the RF
model, the highest AUROCs were observed for family (median AUROC:
0.687), genus (median AUROC: 0.686), and OTU (median AUROC: 0.698) level
data with no significant difference between the three (Figure 1).
Performance with ASVs (median AUROC: 0.676) was significantly lower than
OTU and genus (p \textless{} 0.05) but not family level (p = 0.06).
These results were consistent for ASVs generated with DADA2 \{\} (median
AUROC: 0.66). These results suggest that finer taxonomic resolution is
not necessarily better for differentiating a persons cancer status from
the microbiome.

One hypothesis for the observation that model performance increases from
phylum to OTU level then drops slightly at ASV level is that at higher
taxonomic levels (e.g.~phylum) there are too few taxa and too much
overlap to reliably differentiate between cases and controls. At the
level of genus/OTU data there is enough data and variation but at the
ASV level, the data is too specific to individuals and doesn't overlap
enough. Examination of the prevalence of taxa in samples at each level
supports this idea. A majority of taxa are present in greater than 75\%
of samples at the phylum (67\% of taxa) and class (63\% of taxa)
levels). The opposite is observed at the OTU and ASV level where 60\%
and 53\% of taxa respectively are only present in less than 25\% of
samples (Supplemental Figure 2). While the resolution provided by ASVs
is useful in

@@

@@

These results demonstrate that consideration of the appropriate
taxonomic resolution for utilizing the microbiome as a predictive tool.
In general, we found that finer resolution (e.g.~ASVs) does not add
additional sensitivity to model predicition and at the ASV level
actually impedes model performance due to the sparsity of shared taxa.

@@

\includegraphics[width=0.75\textwidth,height=\textheight]{../exploratory/figures/rf_with_stats.png}

\textbf{Figure 1: Random Forest Model Performance with Significance.}
Boxplots of AUROC values on the test dataset for 100 seeds predicting
SRNs using a Random Forest model. Dashed line denotes AUROC of 0.5 which
is equivalent to random classification. Significance between taxonomic
levels was quantified by comparing the difference in mean AUROC and is
denoted by letters A through E on the right side of the plot; taxonomic
levels with the same letter are in the same significance group and are
not significantly different from one another.

@@

\begin{longtable}[]{@{}lrrc@{}}
\toprule
Taxonomic Level & Number of Features &
\makecell[c]{Number of Features \\ After Preprocessing} &
\makecell[c]{Percent of Features Kept \\ After Preprocessing} \\
\midrule
\endhead
Phylum & 19 & 9 & 47.4 \% \\
Class & 36 & 19 & 52.8 \% \\
Order & 65 & 28 & 43.1 \% \\
Family & 124 & 54 & 43.5 \% \\
Genus & 316 & 115 & 36.4 \% \\
OTU & 20079 & 705 & 3.5 \% \\
ASV & 104106 & 478 & 0.5 \% \\
\bottomrule
\end{longtable}

@@

\includegraphics[width=\textwidth,height=0.5\textheight]{../exploratory/figures/bin_prevalence.png}\\
\textbf{Supplemental Figure 2: Prevalence of Taxa in Samples.}
Distribution of taxa prevalence in samples at each taxonomic level.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-callahan2017}{}%
Callahan, Benjamin J., Paul J. McMurdie, and Susan P. Holmes. 2017.
{``Exact Sequence Variants Should Replace Operational Taxonomic Units in
Marker-Gene Data Analysis.''} \emph{The ISME Journal} 11 (12): 2639--43.
\url{https://doi.org/10.1038/ismej.2017.119}.

\leavevmode\hypertarget{ref-garcuxeda2011a}{}%
García, Gimeno, and Antonio Z. 2011. {``Factors Influencing Colorectal
Cancer Screening Participation.''} \emph{Gastroenterology Research and
Practice} 2012 (December): e483417.
\url{https://doi.org/10.1155/2012/483417}.

\leavevmode\hypertarget{ref-siegel2020}{}%
Siegel, Rebecca L., Kimberly D. Miller, Ann Goding Sauer, Stacey A.
Fedewa, Lynn F. Butterly, Joseph C. Anderson, Andrea Cercek, Robert A.
Smith, and Ahmedin Jemal. 2020. {``Colorectal Cancer Statistics,
2020.''} \emph{CA: A Cancer Journal for Clinicians} 70 (3): 145--64.
https://doi.org/\url{https://doi.org/10.3322/caac.21601}.

\leavevmode\hypertarget{ref-topuxe7uolu2020}{}%
Topçuoğlu, Begüm D., Nicholas A. Lesniak, Mack T. Ruffin, Jenna Wiens,
and Patrick D. Schloss. 2020. {``A Framework for Effective Application
of Machine Learning to Microbiome-Based Classification Problems.''}
\emph{mBio} 11 (3). \url{https://doi.org/10.1128/mBio.00434-20}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Colorectal cancer is one of the most common cancers in men and women and
a leading cause of cancer related deaths in the United States
(\protect\hyperlink{ref-siegel2020}{1}). Early detection and treatment
are essential to increase survival rates, but for a variety of reasons
including the invasiveness and high cost of screening
(i.e.~colonoscopy), many people do not comply with recommended screening
guidelines (\protect\hyperlink{ref-garcuxeda2011a}{2}) prompting a need
for low cost, non-invasive detection methods. A growing body of research
points to the gut microbiome as a promising target for non-invasive
screening to detect screen relevant neoplasias (neoplasms?) (SRNs)
consisting of pre-cancerous polyps (i.e.~advanced adenomas) and
carcinomas. Efforts to realize the diagnostic potential of the gut
microbiome in detecting SRNs have focused on machine learning (ML)
methods using abundances from operational taxonomic unit (OTU)
classifications based on amplicon sequencing of the 16S rRNA gene \{\}.
However, whether this is the optimal taxonomic resolution for
classifying SRNs from microbiome data is unknown. Additionally, recent
work has pushed for the use of amplicon sequence variants (ASVs) to
replace OTUs for marker-gene analysis because of the improved resolution
with ASVs (\protect\hyperlink{ref-callahan2017}{3}). However, whether
the additional resolution provided by ASVs is useful for ML
classification is unclear \{pat preprint?\}. Since ML classification
relies on consistent differences between groups, its possible that the
resolution at the ASV level is too individualized to accurately
differentiate groups. Topçuoğlu \emph{et al}
(\protect\hyperlink{ref-topuxe7uolu2020}{4}) recently demonstrated
effective application of machine learning (ML) to microbiome based
classification problems and developed a framework for applying ML
practices in a more reproducible way (mikropml). This analysis utilizes
the reproducible framework developed by Topçuoğlu \emph{et al} to
quantify which ML method and taxonomic level produce the best performing
classifier for detecting SRNs from microbiome data.

@@

Utilizing publicly available 16S rRNA sequence data from stool of
patients with SRNs and healthy controls, we generated abundance tables
with Mothur \{\} annotated to Phylum, Class, Order, Family, Genus, OTU
and ASV levels. Using the taxonomic abundance data, we quantified how
accurately samples could be classified as ``normal'' or ``SRN''
(i.e.~advanced adenoma or carcinoma) using five machine learning methods
with the Mikropml R package (methods). Across the five machine learning
methods tested, model performance tended to increase with taxonomic
level usually peaking around genus/OTU level before dropping off
slightly with ASVs (Supplemental Figure 1). Random forest (RF) was
consistently the top performer at most taxonomic levels. Within the RF
model, the highest AUROCs were observed for family (median AUROC:
0.687), genus (median AUROC: 0.686), and OTU (median AUROC: 0.698) level
data with no significant difference between the three (Figure 1).
Performance with ASVs (median AUROC: 0.676) was significantly lower than
OTU (p \textless{} 0.01), but borderline equivalent to family (p = 0.06)
and genus (p = 0.05) levels. These results were consistent for ASVs
generated with DADA2 (\protect\hyperlink{ref-callahan2016}{5}) (median
AUROC: 0.66). These results suggest that finer taxonomic resolution is
not necessarily better for differentiating a persons cancer status from
the microbiome.

While AUROC values between models is a useful way to compare the overall
model performance across all thresholds, they can be misleading
(\protect\hyperlink{ref-lobo2008}{6}). Depending on the intended
implementation of the model, one may want to optimize the true-positive
rate(or sensitivity) over the false-postivite rate (or specificity). To
further compare the model performance across taxonomic levels we
compared the sensitivity of the models

\begin{itemize}
\tightlist
\item
  on average, how many positives are missed with ASV?
\end{itemize}

One hypothesis for the observation that model performance increases from
phylum to OTU level then drops slightly at ASV level is that at higher
taxonomic levels (e.g.~phylum) there are too few taxa and too much
overlap to reliably differentiate between cases and controls. At the
level of genus/OTU data there is enough data and variation but at the
ASV level, the data is too specific to individuals and doesn't overlap
enough. Examination of the prevalence of taxa in samples at each level
supports this idea. A majority of taxa are present in greater than 75\%
of samples at the phylum (67\% of taxa) and class (63\% of taxa) levels.
The opposite is observed at the OTU and ASV level where 60\% and 53\% of
taxa respectively are only present in less than 25\% of samples
(Supplemental Figure 3). While the resolution provided by ASVs is useful
in

@@

Mikropml\{\}

@@

These results demonstrate that consideration of the appropriate
taxonomic resolution for utilizing the microbiome as a predictive tool.
In general, we found that finer resolution (e.g.~ASVs) does not add
additional sensitivity to model prediction and at the ASV level actually
impedes model performance due to the sparsity of shared taxa.

@@

\includegraphics{manuscript_files/figure-latex/fig1-1.pdf}

\textbf{Figure 1: Random Forest Model Performance.} \textbf{A)} Boxplots
with points of area under the receiver operating characteristic curve
(AUROC) values on the test dataset for 100 seeds predicting SRNs using a
Random Forest model. Dashed line denotes AUROC of 0.5 which is
equivalent to random classification. Significance between taxonomic
levels was quantified by comparing the difference in mean AUROC and is
denoted by letters A through E on the right side of the plot; taxonomic
levels with the same letter are in the same significance group and are
not significantly different from one another. \textbf{B)} Strip plot of
the sensitivity at a specificity of 90\% across the 100 model
iterations. Black points denote the median and the lines denote the IQR.
The letters W through Z denote the significance groups.

@@

\begin{longtable}[]{@{}lrrc@{}}
\toprule
Taxonomic Level & Number of Features &
\makecell[c]{Number of Features \\ After Preprocessing} &
\makecell[c]{Percent of Features Kept \\ After Preprocessing} \\ \addlinespace
\midrule
\endhead
Phylum & 19 & 9 & 47.4 \% \\ \addlinespace
Class & 36 & 19 & 52.8 \% \\ \addlinespace
Order & 65 & 28 & 43.1 \% \\ \addlinespace
Family & 124 & 54 & 43.5 \% \\ \addlinespace
Genus & 316 & 115 & 36.4 \% \\ \addlinespace
OTU & 20079 & 705 & 3.5 \% \\ \addlinespace
ASV & 104106 & 478 & 0.5 \% \\ \addlinespace
\bottomrule
\end{longtable}

@@

\includegraphics[width=\textwidth,height=0.5\textheight]{../exploratory/figures/roc_by_level.png}

\textbf{Supplemental Figure 2: Averaged ROC curves} ROC curves averaged
across the 100 iterations of the model. The shaded region represents the
standard deviation form the mean.

\includegraphics[width=\textwidth,height=0.45\textheight]{../exploratory/figures/bin_prevalence.png}\\
\textbf{Supplemental Figure 3: Prevalence of Taxa in Samples.}
Distribution of taxa prevalence in samples at each taxonomic level.

\includegraphics[width=\textwidth,height=0.85\textheight]{../exploratory/figures/top10_imp.png}\\
\textbf{Supplemental Figure 4: Top 10 important taxa at each taxonomic
level.} Summary of the 10 most important taxa for the random forest
models at each taxonomic level based on the average decrease in AUC when
the feature is permuted.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{1}
\leavevmode\hypertarget{ref-siegel2020}{}%
\CSLLeftMargin{1. }
\CSLRightInline{\textbf{Siegel RL}, \textbf{Miller KD}, \textbf{Sauer
AG}, \textbf{Fedewa SA}, \textbf{Butterly LF}, \textbf{Anderson JC},
\textbf{Cercek A}, \textbf{Smith RA}, \textbf{Jemal A}. 2020. Colorectal
cancer statistics, 2020. CA: A Cancer Journal for Clinicians
\textbf{70}:145--164. doi:\url{https://doi.org/10.3322/caac.21601}.}

\leavevmode\hypertarget{ref-garcuxeda2011a}{}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{García G}, \textbf{Z A}. 2011. Factors
Influencing Colorectal Cancer Screening Participation. Gastroenterology
Research and Practice \textbf{2012}:e483417.
doi:\href{https://doi.org/10.1155/2012/483417}{10.1155/2012/483417}.}

\leavevmode\hypertarget{ref-callahan2017}{}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{Callahan BJ}, \textbf{McMurdie PJ},
\textbf{Holmes SP}. 2017. Exact sequence variants should replace
operational taxonomic units in marker-gene data analysis. The ISME
Journal \textbf{11}:2639--2643.
doi:\href{https://doi.org/10.1038/ismej.2017.119}{10.1038/ismej.2017.119}.}

\leavevmode\hypertarget{ref-topuxe7uolu2020}{}%
\CSLLeftMargin{4. }
\CSLRightInline{\textbf{Topçuoğlu BD}, \textbf{Lesniak NA},
\textbf{Ruffin MT}, \textbf{Wiens J}, \textbf{Schloss PD}. 2020. A
Framework for Effective Application of Machine Learning to
Microbiome-Based Classification Problems. mBio \textbf{11}.
doi:\href{https://doi.org/10.1128/mBio.00434-20}{10.1128/mBio.00434-20}.}

\leavevmode\hypertarget{ref-callahan2016}{}%
\CSLLeftMargin{5. }
\CSLRightInline{\textbf{Callahan BJ}, \textbf{McMurdie PJ},
\textbf{Rosen MJ}, \textbf{Han AW}, \textbf{Johnson AJA}, \textbf{Holmes
SP}. 2016. DADA2: High-resolution sample inference from Illumina
amplicon data. Nature Methods \textbf{13}:581--583.
doi:\href{https://doi.org/10.1038/nmeth.3869}{10.1038/nmeth.3869}.}

\leavevmode\hypertarget{ref-lobo2008}{}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Lobo JM}, \textbf{Jiménez-Valverde A},
\textbf{Real R}. 2008. AUC: a misleading measure of the performance of
predictive distribution models. Global Ecology and Biogeography
\textbf{17}:145--151.
doi:\href{https://doi.org/10.1111/j.1466-8238.2007.00358.x}{10.1111/j.1466-8238.2007.00358.x}.}
